I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-02 Paper/Paper_noProof.tex
abstract

\title{Diamond and Vericompensate}
\date{}

@@

>>>>

\title{I Compensate, therefore I Am \\ (accurate for DNN verification)}
\date{}

@@

\begin{abstract}
  Deep Neural Networks (DNNs) verification is now a mature research field, with many methodologies and tools to verify formaly  that they are correct, with an annual competition to compare them, etc. Formally, the question is, given a DNN and a property to check, does the property hold over a set of inputs of the DNN. This allows e.g. to check local robustness around an input $I$, by checking that the i-th output neuron has the largest weight among all output neurons uniformly over a neighbourhood around $I$.
  In the most recent years, the focus has been on combining several of these efficient techniques to optimize the speed/accuracy trade-offs (branch and bound, multi neuron encoding, milp encoding). While some relatively large DNNs (tens of thousands of neurons) can be checked very efficiently with modern tools, 
  some smaller DNNs (hundreds of neurons) are still paradoxally challenging to address with efficient algorithms.

  In this paper, we analyze efficient DNNs algorithm based on abstraction (DeepPoly, PRIMA, different version of Crown), and uncover the main reason for the loss of accuracy, namely compensation. Intuitively, a compensation happens when there are 2 paths 
   Based on this finding, we propose a novel methodology to obtain interesting trade-offs in terms of speed/accuracy.
\end{abstract}
